

\documentclass[letterpaper,10pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{titlesec}
\usepackage{boldline}
\usepackage{bold-extra}
%\usepackage[default]{lato}
\usepackage[sfdefault,light]{roboto}
%\renewcommand{\familydefault}{\sfdefault}
\usepackage[T1]{fontenc}

\usepackage[outline]{contour}% http://ctan.org/pkg/contour
\contourlength{0.1pt}
\contournumber{10}%


%-----------------------------------------------------------


\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{10in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.5in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%----------------------------------------------------COMMANDS--------------------------------------------------------------

\newcommand{\resheading}[1]{\vspace{2pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large\scshape #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-8pt}
}

\newcommand{\customitem}[2]{\item[$\bullet$] {
 	\textbf{#1} \hfill \textit{#2}}
 }

\newcommand{\workitem}[4]{
\begin{tabular*}{6.5in}{l @{\extracolsep{\fill}} r}
		\textbf{\textsc{#1}} & \textit{#2} \\
		\textsc{#3} & \textit{#4} \\
\end{tabular*}\vspace{-4pt}}

\newcommand{\educationitem}[5]{
\begin{tabular*}{6.5in}{l @{\extracolsep{\fill}} r}
		\textbf{\textsc{#1}} & \textit{#2} \\
		\textsc{#3} & \textit{#4} \\
		\textit{#5} & \textit{\hfill} \\
\end{tabular*}\vspace{-4pt}}

\newcommand{\workitemfull}[4]{
	\item[$\bullet$]\workitem{#1}{#2}{#3}{#4}
}

\newcommand{\educationitemfull}[5]{
	\item[$\bullet$]\educationitem{#1}{#2}{#3}{#4}{#5}
}

\newcommand{\header}[4]{
\begin{tabular*}{7in}{l @{\extracolsep{\fill}}r}
	\LARGE \textbf {\textsc{#1}} & {\hfill} \\
		Contact : \textit{#2} & {\hfill} \\
		
		Email : \textit{#4} & {\hfill} \\
		LinkedIn : \textit{#3} & {\hfill} \\ 
		
		
	\hlineB{4}	
\end{tabular*}		
}

\newcommand{\keyword}[1]{%
	\contour{black}{\textit{#1}}%
}

%-------------------------------------------------COMMANDS END----------------------------------------------------------

\begin{document}

\header{Gaurav Mishra}{+1 6316525100}{https://www.linkedin.com/in/gaurav-mishra-5822a030}{gamishra@cs.stonybrook.edu}
\vspace{5pt}

%minipage to force block of text on same page
\begin{minipage}{\textwidth}

\resheading{Education}

\begin{enumerate}
	\educationitemfull{Stony Brook University}{Sept 2016 - Dec 2017}{MS , Computer Science}{Stony Brook,USA}{GPA = 3.8/4}
	\educationitemfull{Indian Institute Of Technology,Varanasi}{May 2006 - Apr 2010}{Btech , Computer Science}{Varanasi,India}{CGPA = 7.2/10}
\end{enumerate}

\end{minipage}

%
%\resheading{Skill Set}
%\begin{enumerate}
%\item[-] \textbf{Languages} - Java , Javascript , NodeJs , C++ , ActionScript3 , Python , PHP
%\item[-] \textbf{Frameworks} - ExpressJs , Django , ReactJs , DropWizard
%\item[-] \textbf{Advanced Courses Taken} - Computer Vision , Computer Graphics, Machine learning , Data Science 
%\end{enumerate}
%
\resheading{Work Experience}
\begin{enumerate}
	\workitemfull{ThousandEyes}{Feb 2018 - Present}{Software Engineer}{San Francisco, USA}
	\begin{enumerate}
		\item[-] Designing, implementing and maintaining components of our data processing pipeline. These components include micro services for receiving data points from agents, processing them and finally storing them in a distributed data store.
		\item[-] Implementing new user flows in our web application which exposes our agent’s new capabilities to customers.
		\item[-] Work on data visualization component of our web interface. 
		\item[-] Expose new apis to customers which allow users to interact with our platform from outside web interface.
		\item[-] \textbf{Tech Stack} - Java, Javascript, Spring boot, Mysql, Kafka, ElasticSearch, Angular1, Docker, Kubernetes
	\end{enumerate}
	\workitemfull{Google}{May 2017 - August 2017}{Software Intern}{Kirkland , USA}
	\begin{enumerate}
		\item[-] Working in Ads Team , owned and developed troubleshooting features for Double Click Manager.  
		\item[-] Using machine learning try to predict if a line item's current settings will perform well on ad exchange server.
		\item[-] \textbf{Tech Stack} - Java, Angular Dart, Spanner, St-cache, Tensor Flow.
	\end{enumerate}
	%typito
	\workitemfull{Typito}{Apr 2015 - July 2016}{Co-Founder/Engineer}{Bangalore,India}
	\begin{enumerate}
		\item[-] Designed and built typito's backend which included the webapps and a couple of downstream video rendering micro services.
		\item[-] Built video rendering engine using Ffmpeg's library. This module was responsible for overlaying graphics animations on top of a video.
		\item[-] Built a micro service for transforming graphics animation created on typito's UI to
		series of png images.
		\item[-] \textbf{Tech Stack} - Javascript/Nodejs, Express,C++, ReactJs, Ffmpeg, Amazon SQS, Amazon Elastic Transcoder, Phantomjs
	\end{enumerate}

	%tivamo	
	\workitemfull{Tivamo}{Aug 2014 - July 2016}{Tech Lead}{Bangalore,India}
	\begin{enumerate}
		\item[-] Built video streaming infrastructure capable of streaming live video broadcasts or video on demand using Wowza media server . delivery protocols being hls and rtmp.
		\item[-] To cut down on infra cost prototyped use of nginx server as edge servers and Wowza as origin server. 
		\item[-] For reducing latency prototyped infra based on WebRTC technologies (Kurento Media Server). 
		\item[-] \textbf{Tech Stack} - Java, Javascript, Wowza, Kurento
	\end{enumerate}	
		
	%playdom
	\workitemfull{Disney (Playdom) }{Jun 2011-Mar 2014}{Senior Software Engineer}			{Bangalore,India}
	\begin{enumerate}
		\item[-] Worked on end to end feature development of 4 social games for facebook . one of 		which was released for IOS and Android too.
		\item[-] Wrote a tool to convert swf file to a texture atlas which could be used by framework 			Starling to render UI using GPU.
	\end{enumerate}	
	
	%infosys
	\workitemfull{Infosys}{June 2010-May 2011}{Junior Research Associate}{Bangalore,India}
	\begin{enumerate}
		\item[-] Worked on Semantic Engine that could process a given english text and store it in a 		format which we could query later using natural language.
		\item[-] Prototyped a application that could process a legal document and guess which parts 		of the document are potential headnotes.A Patent was also filed for the same.
	\end{enumerate}
	
	\workitemfull{IBM}{Apr 2009 - June 2009}{Test Engineer Intern}{Bangalore,India}
	\begin{enumerate}
		\item[-] Worked on automation of manual test cases using IBM's Rational Functional Tester.
		\item[-] Wrote a Module which using character recognition was able to automate 	certain test cases that were not possible using RFT alone.
	\end{enumerate}
\end{enumerate}


\begin{minipage}{\textwidth}
\resheading{Patents}
	\begin{enumerate}
		\item[$\bullet$]Automation of Headnote Extraction from a legal documents.\\ (http://www.google.com/patents/US20130238316)
	\end{enumerate}

\end{minipage}
\end{document}
